### 2017-04-01 paper/evaluation.tex
minor changes on description of setup: considering double-blindness and other minor tweaks

To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel
processor machine with eight virtual CPUs (four cores with two native
threads each) and 16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr
(64-bit version).  Software settings include \Comment{the Linux
\emph{sysstat} package to measure performance, }git to fetch subjects,
Java 8 and Maven 3.3.9 to build and test subjects. Our evaluation
scripts depends on Python 3.4 and Bash to execute and R to analyze the
data.  For replication, all source artifacts are publicly available at
\Fix{create gh-pages}, including supporting scripts (\eg, the script
that test subjects and generates the raw data), and the full list of
projects. \Comment{, and a \emph{Vagrantfile} to emulate our hardware
and all software dependencies.}

>>>>

To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel
processor machine with eight virtual CPUs (four cores with two native
threads each) and 16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr
(64-bit version).  Software settings include \Comment{the Linux
  \emph{sysstat} package to measure performance, }git to fetch
subjects, Java 8, and Maven 3.3.9 to build and test subjects. We used
Python 3.4, Bash, and R to process the data and generate plots.  All
source artifacts are publicly available (on request) for
replication\Comment{ at \Fix{create gh-pages}}.  This includes
supporting scripts (\eg, the script that test subjects and generates
the raw data), and the full list of projects. \Comment{, and a
  \emph{Vagrantfile} to emulate our hardware and all software
  dependencies.}
